Adopting agile in the large: motivations, success factors and challenges

### 2014-04-25 journal/article.tex
Communication and collaboration issues

        \multicolumn{3}{l}{\rule{0pt}{4ex} Communication issues}  \\

@@

The reasons to change were are grouped in three top-level categories: external
issues, internal issues, and communication issues. External issues are related
to the business area which the organization is operating in. Internal issues are
related to the way the organization is managed and software is being developed.
Communication issues represent problems in communication and coordination in
software projects.

@@

Yet another frequent external factor driving for change was the need to
accomodate change during development. Organizations saw agile as a opportunity
to improve responsiveness to change in general [P25, P26, P42].
Some organizations faced difficulties when changes to plans were needed. For
instance, the organizational struture made adapting to changes difficult [52],
and making changes created management overhead [P51]. Other organizations saw an
business advantage if priorities could be changed as required [P8, P39].
Customers and business representatives were in many cases attributed as the
sources of change requests, and the responsiveness to customer requests needed
to be improved [P18, P33, P36, P49].

@@

Command and control style management where ``a few people, usually those
farthest from the action, made the decisions without directly involving the
developers doing the actual work'' [P44] was brought up as a problem. For
instance, schedules could be dictated by management, and teams had to comply to
them regardless of the workload [P9]. As a result teams were overworked and
needed stretch far to finish projects on time. Low morale and motivation were
identified as problems that needed to be fixed, and agile was seen as a solution
[P25, P30, P40].

@@

>>>>

        \multicolumn{3}{l}{\rule{0pt}{4ex} Communication and collaboration issues}  \\

@@

The reasons to change were are grouped in three top-level categories: external
issues, internal issues, and communication issues. External issues are related
to the business area which the organization is operating in. Internal issues are
related to the way the organization is managed and software is being developed.
Communication and collaboration issues are related to internal and external
collaboration. Change was motivated by known problems in these categories, such
as known process dysfunctions or communication problems. There was also internal
and external demand for improvement, for instance in speed of delivery and
quality.

@@

Yet another frequent external factor driving for improvement was the need to
accomodate change during development. Organizations saw agile as a opportunity
to improve responsiveness to change in general [P25, P26, P42].
Some organizations faced difficulties when changes to plans were needed. For
instance, the organizational struture made adapting to changes difficult [52],
and making changes created management overhead [P51]. Other organizations saw an
business advantage if priorities could be changed as required [P8, P39].
Customers and business representatives were in many cases attributed as the
sources of change requests, and the responsiveness to customer requests needed
to be improved [P18, P33, P36, P49].

@@

Command and control style management where ``a few people, usually those
farthest from the action, made the decisions without directly involving the
developers doing the actual work'' was highlighted as a problem [P44]. For
instance, schedules could be dictated by management, and teams had to comply to
them regardless of the workload [P9]. As a result teams were overworked and
needed stretch far to finish projects on time. Low morale and motivation were
identified as problems that needed to be fixed, and agile was seen as a solution
[P25, P30, P40].

@@

\subsubsection{Communication and collaboration issues}

Many organizations experienced problems in communication and collaboration
between projects, teams, and even members of a single team [P38, P21].
Teams were in many cases organized around components and were working in silos.
Working in silos diluted focus and made adapting to change difficult, as teams
could only focus on their limited area of expertise [P7]. Functional silos acted
against creating a shared purpose in operating [P40], and resulted in a ``ball
over the wall'' mentality [P46]. Distance between teams was also created by
document driven communication, and was causing misunderstanding of requirements
[P24].

Other communication issues were related to requirements handling and difficulty
to focus on the most important aspects of a delivery.
Examples on problems with requirements was too much focus on the documenting
aspect instead of providing understanding [P24, P49], and ignoring the fact that
requirements and understanding are evolving during a project [P4].
In some cases the organization of work and management was such that it hindered
focusing the development [P7], and prioritization of what to work on was not
done efficiently [P38, P39].

--> Demand of better customer collaboration

A few organizations were experiencing rise of agile methods at grass roots
level, but early use of agile resluted in problems when the organization used a
waterfall method on the top level. Tensions arose when teams using different
development approaches attempted to collaborate on products [P10]. On a team
level agile had enabled some flexibility, but that flexibility could not be
leveraged on the scale of the entire organization [P26]. This kind of
experiences drove the organization to deploy agile on a full scale.

%%%%%%%%%%%%%%

% ----------------------------------------------------------------
